---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
The data is loaded from unzipped .csv file 
```{r}
activity <- read.csv("activity.csv", head = TRUE)

```


## What is mean total number of steps taken per day?
Summarizing steps by each day
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
steps.n <- activity %>% group_by(date) %>% summarise(steps = sum(steps))
```

Histogram of the steps amount per day
```{r warning=FALSE}
ggplot(steps.n, aes(steps))+geom_histogram(bins = 10)
```

Mean value of steps per day
```{r}
mean(steps.n$steps, na.rm=TRUE)
```

Median value of steps per day
```{r}
median(steps.n$steps, na.rm=TRUE)
```

## What is the average daily activity pattern?

Summarizing steps per interval
```{r}
steps.interval <- activity %>% group_by(interval) %>% summarize(steps = mean(steps, na.rm = TRUE))
```

Time series plot, showing average number of steps taken per 5-minute interval, averaged across all days
```{r}
plot(x=steps.interval$interval, y=steps.interval$steps, type = "l", main = "Average number of steps taken", xlab = "Interval Number", ylab = "Number of Steps")
```

Interval, containing maximum number of steps (on average across the days)
```{r}
steps.interval[which.max(steps.interval$steps),]$interval
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
